\chapter{List of Publications}
\interfootnotelinepenalty=10000

\begin{enumerate} % [leftmargin=0pt,labelsep=.6in]
\nohyphens{


\item {\em Repeated quantum error correction on a continuously encoded qubit by real-time feedback.} \\
J.~Cramer, N~Kalb, M.A.~Rol, B.~Hensen, M.S.~Blok, M.~Markham, D.J.~Twitchen, R.~Hanson and T.H.~Taminiau. \\
\textit{In preparation}.

\item {\em Optimized quantum sensing with a single electron spin using real-time adaptive measurements.} \\
C. Bonato$^*$, M.S. Blok$^*$, H.T. Dinani, D. Berry, M.~Markham, D.J.~Twitchen, R. Hanson. \\
Nature Nanotechnology \textit{In press}, doi:10.1038/nnano.2015.261 (2015).
{\renewcommand{\thefootnote}{}\footnote{$^*$Equally contributing authors}}

\item {\em Loophole-free Bell inequality violation using electron spins separated by 1.3 kilometres.}
B.~Hensen, H.~Bernien, A.E.~Dréau, A.~Reiserer, N.~Kalb, M.S.~Blok, J.~Ruitenberg, R.F.L.~Vermeulen, R.N.~Schouten, C.~Abellán, W.~Amaya, V.~Pruneri, M.W.~Mitchell, M.~Markham, D.J.~Twitchen, D.~Elkouss, S.~Wehner, T.H.~Taminiau and R.~Hanson. \\ 
Nature \textit{In press}, doi:10.1038/nature15759 (2015).

\item {\em Towards quantum networks of single spins: analysis of a quantum memory with optical interface in diamond.}\\
M.S.~Blok$^*$,N.~Kalb$^*$, A.~Reiserer, T.H.~Taminiau and R.~Hanson.  \\
Faraday Discussions \textit{Advanced online publication}, doi:10.1039/c5fd00113g (2015).

\item  {\em Unconditional quantum teleportation between distant solid-state qubits.} \\
W.~Pfaff, B.~Hensen, H.~Bernien, S.~van Dam, M.S.~Blok, T.H.~Taminiau, M.J.~Tiggelman, R.S.~Schouten, M.~Markham, D.J.~Twitchen, and R.~Hanson.\\
Science \textbf{345}, 532-535 (2014).

\item {\em Manipulating a qubit through the backaction of sequential partial measurements and real-time feedback.} \\
 M.S.~Blok$^*$, C.~Bonato$^*$, M.L.~Markham, D.J.~Twitchen, V.V.~Dobrovitski and R.~Hanson.  \\
Nature Physics \textbf{10}, 189-193 (2014).

\item {\em Heralded entanglement between solid-state qubits separated by three meters.} \\
H.~Bernien, B.~Hensen, W.~Pfaff, G.~Koolstra, M.S.~Blok, L.~Robledo, T.H.~Taminiau, M.~Markham, D.J.~Twitchen, L.~Childress, and R.~Hanson. \\
 Nature \textbf{497}, 86 (2013).

\item {\em Opening up three quantum boxes causes classically undetectable wavefunction collapse.}\\ 
R.E.~George, L.~Robledo, O.J.E.~Maroney, M.S.~Blok, H.~Bernien, M.~Markham, D.J.~Twitchen, J.J.L.~Morton, G.A.D.~Briggs, and R.~Hanson. \\
 Proceedings of the National Academy of Sciences \textbf{110}, 3777 (2013).
\clearpage
\item {\em Decoherence-protected quantum gates for a hybrid solid-state spin register.} \\
T.~van der Sar, Z.H.~Wang, M.S.~Blok, H.~Bernien, T.H.~Taminiau, D.M.~Toyli, D.A.~Lidar, D.D.~Awschalom, R.~Hanson, and V.V.~Dobrovitski. \\ 
Nature \textbf{484}, 82 (2012).

\item {\em Controlling the quantum dynamics of a mesoscopic spin bath in diamond.} \\
G.~de Lange, T.~van der Sar, M.S.~Blok, Z.H.~Wang, V.V.~Dobrovitski and R.~Hanson. \\
 Scientific Reports \textbf{2}, 382 (2012).
}




\end{enumerate}