\documentclass[9pt,a5paper]{memoir}
\usepackage{libertine}
\usepackage[T1]{fontenc}
\usepackage[libertine]{newtxmath}
\usepackage{microtype}
\nofiles
\settypeblocksize{18cm}{13cm}{*}
\setlrmarginsandblock  {*}{12mm}{*}
\setulmarginsandblock  {18mm}{22mm}{*}
\setheadfoot           {5mm}{11mm}
\setheaderspaces       {*}{5.5mm}{*}
\setlength{\parindent} {2em}
\setlength{\parskip}   {0.5\baselineskip}
\checkandfixthelayout
%\setheaderspaces{*}{-15mm}{*}

\begin{document}
\thispagestyle{empty}
\begin{center}
\LARGE{\textbf{Propositions}}\\[11pt]
\large{Belonging to the PhD thesis of Machiel Sebastiaan Blok}\\[11pt]
\large{\textbf{Quantum measurement and real-time feedback \\
\noindent with a spin register in diamond}}\\[11pt]
\end{center}

\noindent
\begin{enumerate}

\item Measurements and feedback can be used to prepare a particle in a desired quantum state. (Chapter 3 of this thesis)

\item The sensitivity of a quantum sensor that is based on a Ramsey interferometry experiment can be improved with real-time feedback techniques. (Chapter 4 of this thesis)

\item The first quantum repeater will be demonstrated with NV centers because it has a quantum memory at its disposal.

\item The quantum measurement problem will not be resolved if experimental physicists refuse to discuss it over lunch.

\item In a system where politicians are judged solely based on the public opinion, big problems for society such as climate change will be solved less efficiently compared to a system where politicians are judged based on predetermined and measurable goals.

\item Calling an argumentation or derivation `trivial' in scientific literature is a sign of disrespect to the reader.

\item The critics of \texitit{rendementsdenken} (making decisions based on yield) will reach their goals faster if they focus on redefining the term yield, as opposed to focusing on eliminating \texitit{rendementsdenken}.

\item Performing experiments is very addictive and can cause serious damage to you and those around you.

\item If nature wanted us to understand quantum mechanics, she would have explained it better. (after a quote from J. Cruijff)
\end{enumerate}

\vspace{\stretch{1}}

\noindent
These propositions are regarded as opposable and defendable, and have been approved as such by the supervisor Prof.~dr.~ir.~R.~Hanson.

\newpage

\thispagestyle{empty}
\begin{center}
\LARGE{\textbf{Stellingen}}\\[11pt]
\large{Behorende bij het proefschrift van Machiel Sebastiaan Blok}\\[11pt]
\large{\textbf{Quantum measurement and real-time feedback \\
\noindent with a spin register in diamond}}\\[11pt]
\end{center}

\noindent
\begin{enumerate}
\item Met metingen en terugkoppeling kan een deeltje in een gewenste quantum toestand gebracht worden. (Hoofdstuk 3 van dit proefschrift)

\item De gevoeligheid van een quantum sensor gebaseerd op een Ramsey interferometrie experiment kan worden vergroot met terugkoppeling technieken. (Hoofdstuk 4 van dit proefschrift)

\item Dankzij de beschikbaarheid van een quantum geheugen zal de eerste quantum repeater gedemonstreerd worden met NV centra.

\item Het quantum meetprobleem zal niet worden opgelost als experimenteel natuurkundigen weigeren om het te bespreken tijdens de lunch.

\item In een systeem waarin politici alleen beoordeeld worden op basis van de publieke opinie zullen grote maatschappelijke problemen zoals klimaatverandering minder effici\"{e}nt worden opgelost dan wanneer politici beoordeeld worden op basis van vooraf bepaalde meetbare doelen.

\item Het aanduiden van een redenering of afleiding als `triviaal' in de wetenschappelijke literatuur getuigt van weinig respect voor de lezer.

\item De criticasters van het rendementsdenken zullen hun doel sneller bereiken wanneer ze zich richten op een herdefini\"{e}ring van het begrip rendement, ipv op het afschaffen van het rendementsdenken.

\item Experimenteren werkt zeer verslavend en kan u en anderen ernstige schade toebrengen.

\item Als de natuur zou willen dat we de quantum mechanica begrepen dan had ze het wel beter uitgelegd. (naar een uitspraak van J. Cruijff)	
\end{enumerate}

\vspace{\stretch{1}}

\noindent
Deze stellingen worden opponeerbaar en verdedigbaar geacht en zijn als zodanig goedgekeurd door de promotor Prof.~dr.~ir.~R.~Hanson.

\end{document}
